---
title: "05_biweekly_epsilon-Lipid1-Lipid2_modeling"
author: "Antonia_Klatt"
date: "2024-08-01"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)

Sys.setlocale("LC_ALL", "English")

#loading packages

library(readr)
library(here)
library(dplyr)
library(ggplot2)
library(cowplot)


#import data (this study)

## epsilon lipid1/lipid2 values

epsilon_lipid1.2 <- read.csv(here("01_Data","epsilon_lipid1_lipid2_ROT19.csv"),
                              header = TRUE , sep = ";" , row.names=  1, stringsAsFactors = FALSE, na.strings = "#NV")

## phytoplankton relative biovolume 

phytoplankton_rel.bioVol <- read.csv(here("01_Data","phytoplankton_rel_biovolume_ROT19.csv"), header = TRUE , sep = ";" , row.names=  1, stringsAsFactors = FALSE, na.strings = "#NV")

## phytoplankton & microzooplankton relative biovolume 

phyto.microplankton_rel.bioVol <- read.csv(here("01_Data","phyto_microplankton_rel_biovolume_ROT19.csv"), header = TRUE , sep = ";" , row.names=  1, stringsAsFactors = FALSE, na.strings = "#NV")

## eukaryotic algae relative biovolume 

eukary.algae_rel.bioVol <- read.csv(here("01_Data","eukaryotic_algae_rel_biovolume_ROT19.csv"), header = TRUE , sep = ";" , row.names=  1, stringsAsFactors = FALSE, na.strings = "#NV")

## eukaryotic algae & microzooplankton relative biovolume 

eukary.algae.microplankton_rel.bioVol <- read.csv(here("01_Data","eukaryotic_algae_microplankton_rel_biovolume_ROT19.csv"), header = TRUE , sep = ";", row.names=  1,  stringsAsFactors = FALSE, na.strings = "#NV")

## d2H water values

d2H.water <- read.csv(here("01_Data","d2H_H2O_ROT19.csv"), header = TRUE , sep = ";" , stringsAsFactors = FALSE, na.strings = "#NV")


#note: data frames include two different depths: surface water (A) and chlorophyll maximum depth (B)


#import data (reference data) 

## alpha lipid/water values algal culturing studies (Ladd et al., 2024) [https://doi.org/10.5061/dryad.nvx0k6f0v]

alpha_lipid_cultures <- read.csv(here("02_Reference_data","alpha_lipid_water_algae_cultures_Ladd_etal_2024.csv"),
                                  header = TRUE , sep = ";" , stringsAsFactors = FALSE, na.strings = "#NV")


## d2H C16:0 values from seston and zooplankton (Pilecky et al., 2022) [https://doi.org/10.1111/1365-2435.13981]

d2H_C16.0_seston_zoo <- read.csv(here("02_Reference_data","d2H_C16.0_FieldStudy_Pilecky_etal_2022.csv"),
                                  header = TRUE , sep = ";" , stringsAsFactors = FALSE, na.strings = "#NV")


#transforming datasets for calculation 

## transform biovolume percentage data to decimals (division by 100)

phyto_rel.bioVol.dec <- phytoplankton_rel.bioVol/100

phyto.micro_rel.bioVol.dec <- phyto.microplankton_rel.bioVol/100

eukary.algae_rel.bioVol.dec <- eukary.algae_rel.bioVol/100

eukary.algae.micro_rel.bioVol.dec <- eukary.algae.microplankton_rel.bioVol/100

## conversion of d2H water values to R water values

R.water <- as.data.frame((d2H.water[,2:2]/1000)+1)

```

## Monte Carlo simulation of alpha lipid/water values for each lipid and phytoplankton group

```{r}

#assuming a normal distribution (N) with mean and SD of alpha lipid/water values from algal cultures (Ladd et al., 2024) (n= 50,000)

## no set.seed function was set for rnorm() to avoid any influence of the set.seed number on the results- 
##instead, n in rnorm() was set to 50,000 to have a high enough sampling number to gain consistent mean values according to the central limit theorem

#N(alpha C16:0-water) 

## cyanobacteria 

mean_alpha_C16_water_cyano <- alpha_lipid_cultures[1:1,2:2]
sd_alpha_C16_water_cyano <- alpha_lipid_cultures[1:1,3:3]

norm_cyano_alpha_C16_water <- rnorm(50000, mean= mean_alpha_C16_water_cyano , sd= sd_alpha_C16_water_cyano)
norm_cyano_alpha_C16_water.df <- as.data.frame(norm_cyano_alpha_C16_water)

## green algae (GA)

mean_alpha_C16_water_GA <- alpha_lipid_cultures[2:2,2:2]
sd_alpha_C16_water_GA <- alpha_lipid_cultures[2:2,3:3]

norm_GA_alpha_C16_water <- rnorm(50000, mean= mean_alpha_C16_water_GA , sd= sd_alpha_C16_water_GA)
norm_GA_alpha_C16_water.df <- as.data.frame(norm_GA_alpha_C16_water)

## Diatoms

mean_alpha_C16_water_dia <- alpha_lipid_cultures[3:3,2:2]
sd_alpha_C16_water_dia <- alpha_lipid_cultures[3:3,3:3]

norm_dia_alpha_C16_water <- rnorm(50000, mean= mean_alpha_C16_water_dia , sd= sd_alpha_C16_water_dia)
norm_dia_alpha_C16_water.df <- as.data.frame(norm_dia_alpha_C16_water)

## Dinoflagellates

mean_alpha_C16_water_dino <- alpha_lipid_cultures[4:4,2:2]
sd_alpha_C16_water_dino <- alpha_lipid_cultures[4:4,3:3]

norm_dino_alpha_C16_water <- rnorm(50000, mean= mean_alpha_C16_water_dino , sd= sd_alpha_C16_water_dino)
norm_dino_alpha_C16_water.df <- as.data.frame(norm_dino_alpha_C16_water)

## Chrysophyta <- based on mean and SD of d2H C16:0 values of diatoms and dinoflagellates 

mean_alpha_C16_water_chryso <- alpha_lipid_cultures[5:5,2:2]
sd_alpha_C16_water_chryso <- alpha_lipid_cultures[5:5,3:3]

norm_chryso_alpha_C16_water <- rnorm(50000, mean= mean_alpha_C16_water_chryso , sd= sd_alpha_C16_water_chryso)
norm_chryso_alpha_C16_water.df <- as.data.frame(norm_chryso_alpha_C16_water)

## Cryptomonads

mean_alpha_C16_water_crypto <- alpha_lipid_cultures[6:6,2:2]
sd_alpha_C16_water_crypto <- alpha_lipid_cultures[6:6,3:3]

norm_crypto_alpha_C16_water <- rnorm(50000, mean= mean_alpha_C16_water_crypto , sd= sd_alpha_C16_water_crypto)
norm_crypto_alpha_C16_water.df <- as.data.frame(norm_crypto_alpha_C16_water)


#N(alpha phytol-water)

## cyanobacteria 

mean_alpha_phytol_water_cyano <- alpha_lipid_cultures[1:1,4:4]
sd_alpha_phytol_water_cyano <- alpha_lipid_cultures[1:1,5:5]

norm_cyano_alpha_phytol_water <- rnorm(50000, mean= mean_alpha_phytol_water_cyano , sd= sd_alpha_phytol_water_cyano)
norm_cyano_alpha_phytol_water.df <- as.data.frame(norm_cyano_alpha_phytol_water)

## green algae (GA)

mean_alpha_phytol_water_GA <- alpha_lipid_cultures[2:2,4:4]
sd_alpha_phytol_water_GA <- alpha_lipid_cultures[2:2,5:5]

norm_GA_alpha_phytol_water <- rnorm(50000, mean= mean_alpha_phytol_water_GA , sd= sd_alpha_phytol_water_GA)
norm_GA_alpha_phytol_water.df <- as.data.frame(norm_GA_alpha_phytol_water)

## Diatoms

mean_alpha_phytol_water_dia <- alpha_lipid_cultures[3:3,4:4]
sd_alpha_phytol_water_dia <- alpha_lipid_cultures[3:3,5:5]

norm_dia_alpha_phytol_water <- rnorm(50000, mean= mean_alpha_phytol_water_dia , sd= sd_alpha_phytol_water_dia)
norm_dia_alpha_phytol_water.df <- as.data.frame(norm_dia_alpha_phytol_water)

## Dinoflagellates

mean_alpha_phytol_water_dino <- alpha_lipid_cultures[4:4,4:4]
sd_alpha_phytol_water_dino <- alpha_lipid_cultures[4:4,5:5]

norm_dino_alpha_phytol_water <- rnorm(50000, mean= mean_alpha_phytol_water_dino , sd= sd_alpha_phytol_water_dino)
norm_dino_alpha_phytol_water.df <- as.data.frame(norm_dino_alpha_phytol_water)

## Chrysophyta <- based on mean and SD of d2H phytol values of diatoms and dinoflagellates

mean_alpha_phytol_water_chryso <- alpha_lipid_cultures[5:5,4:4]
sd_alpha_phytol_water_chryso <- alpha_lipid_cultures[5:5,5:5]

norm_chryso_alpha_phytol_water <- rnorm(50000, mean= mean_alpha_phytol_water_chryso , sd= sd_alpha_phytol_water_chryso)
norm_chryso_alpha_phytol_water.df <- as.data.frame(norm_chryso_alpha_phytol_water)

## Cryptomonads

mean_alpha_phytol_water_crypto <- alpha_lipid_cultures[6:6,4:4]
sd_alpha_phytol_water_crypto <- alpha_lipid_cultures[6:6,5:5]

norm_crypto_alpha_phytol_water <- rnorm(50000, mean= mean_alpha_phytol_water_crypto , sd= sd_alpha_phytol_water_crypto)
norm_crypto_alpha_phytol_water.df <- as.data.frame(norm_crypto_alpha_phytol_water)


#N(alpha sterol-water)

## cyanobacteria #NA #no sterols

## green algae (GA)

mean_alpha_sterol_water_GA <- alpha_lipid_cultures[2:2,6:6]
sd_alpha_sterol_water_GA <- alpha_lipid_cultures[2:2,7:7]

norm_GA_alpha_sterol_water <- rnorm(50000, mean= mean_alpha_sterol_water_GA , sd= sd_alpha_sterol_water_GA)
norm_GA_alpha_sterol_water.df <- as.data.frame(norm_GA_alpha_sterol_water)

## Diatoms

mean_alpha_sterol_water_dia <- alpha_lipid_cultures[3:3,6:6]
sd_alpha_sterol_water_dia <- alpha_lipid_cultures[3:3,7:7]

norm_dia_alpha_sterol_water <- rnorm(50000, mean= mean_alpha_sterol_water_dia , sd= sd_alpha_sterol_water_dia)
norm_dia_alpha_sterol_water.df <- as.data.frame(norm_dia_alpha_sterol_water)

## Dinoflagellates

mean_alpha_sterol_water_dino <- alpha_lipid_cultures[4:4,6:6]
sd_alpha_sterol_water_dino <- alpha_lipid_cultures[4:4,7:7]

norm_dino_alpha_sterol_water <- rnorm(50000, mean= mean_alpha_sterol_water_dino , sd= sd_alpha_sterol_water_dino)
norm_dino_alpha_sterol_water.df <- as.data.frame(norm_dino_alpha_sterol_water)

## Chrysophyta <- based on mean and SD of d2H sterol values of diatoms and dinoflagellates  

mean_alpha_sterol_water_chryso <- alpha_lipid_cultures[5:5,6:6]
sd_alpha_sterol_water_chryso <- alpha_lipid_cultures[5:5,7:7]

norm_chryso_alpha_sterol_water <- rnorm(50000, mean= mean_alpha_sterol_water_chryso , sd= sd_alpha_sterol_water_chryso)
norm_chryso_alpha_sterol_water.df <- as.data.frame(norm_chryso_alpha_sterol_water)

## Cryptomonads

mean_alpha_sterol_water_crypto <- alpha_lipid_cultures[6:6,6:6]
sd_alpha_sterol_water_crypto <- alpha_lipid_cultures[6:6,7:7]

norm_crypto_alpha_sterol_water <- rnorm(50000, mean= mean_alpha_sterol_water_crypto , sd= sd_alpha_sterol_water_crypto)
norm_crypto_alpha_sterol_water.df <- as.data.frame(norm_crypto_alpha_sterol_water)

```

## modeling of biovolume-weighted 2H/1H (R) lipid values for each sampling date considering algal biovolume only

### calculating 2H/1H (R) lipid values for each algal group by R lipid = alpha lipid/water * R water, based on R water values in Rotsee, then multiply with relative biovolume

#### first: R lipid algal group= alpha lipid/water x R water
#### second: R lipid phyto=  Rlipid algal group x bioVol 


```{r}

# modeling R C16:0 values 

## defining relative biovolume of single algal groups 

cyano_phyto_bio1 <- as.data.frame(phyto_rel.bioVol.dec$cyanobacteria_relBio)

GA_phyto_bio1 <- as.data.frame(phyto_rel.bioVol.dec$green.algae_relBio)

chryso_phyto_bio1 <- as.data.frame(phyto_rel.bioVol.dec$Chrysophyta_relBio)

dia_phyto_bio1 <- as.data.frame(phyto_rel.bioVol.dec$Diatoms_relBio)

dino_phyto_bio1 <- as.data.frame(phyto_rel.bioVol.dec$Dinoflagellates_relBio)

crypto_phyto_bio1 <- as.data.frame(phyto_rel.bioVol.dec$Cryptophyceae_relBio)


#cyanobacteria

R_C16_cyano_fun1 <- function(x) (x*norm_cyano_alpha_C16_water.df)

R_C16_cyano_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_C16_cyano_fun1)) 


R_C16_cyano_fun2 <- function(x) (x*cyano_phyto_bio1)

R_C16_cyano_bioVol_biweekly <- as.data.frame(apply((R_C16_cyano_biweekly), MARGIN = 1, FUN = R_C16_cyano_fun2))


## green algae (GA)

R_C16_GA_fun1 <- function(x) (x*norm_GA_alpha_C16_water.df)

R_C16_GA_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_C16_GA_fun1)) 


R_C16_GA_fun2 <- function(x) (x*GA_phyto_bio1)

R_C16_GA_bioVol_biweekly <- as.data.frame(apply((R_C16_GA_biweekly), MARGIN = 1, FUN = R_C16_GA_fun2))


## Chrysophyta

R_C16_chryso_fun1 <- function(x) (x*norm_chryso_alpha_C16_water.df)

R_C16_chryso_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_C16_chryso_fun1)) 


R_C16_chryso_fun2 <- function(x) (x*chryso_phyto_bio1)

R_C16_chryso_bioVol_biweekly <- as.data.frame(apply((R_C16_chryso_biweekly), MARGIN = 1, FUN = R_C16_chryso_fun2))


## Diatoms

R_C16_dia_fun1 <- function(x) (x*norm_dia_alpha_C16_water.df)

R_C16_dia_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_C16_dia_fun1)) 


R_C16_dia_fun2 <- function(x) (x*dia_phyto_bio1)

R_C16_dia_bioVol_biweekly <- as.data.frame(apply((R_C16_dia_biweekly), MARGIN = 1, FUN = R_C16_dia_fun2))


## Dinoflagellates

R_C16_dino_fun1 <- function(x) (x*norm_dino_alpha_C16_water.df)

R_C16_dino_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_C16_dino_fun1)) 


R_C16_dino_fun2 <- function(x) (x*dino_phyto_bio1)

R_C16_dino_bioVol_biweekly <- as.data.frame(apply((R_C16_dino_biweekly), MARGIN = 1, FUN = R_C16_dino_fun2))


## Cryptophyceae

R_C16_crypto_fun1 <- function(x) (x*norm_crypto_alpha_C16_water.df)

R_C16_crypto_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_C16_crypto_fun1)) 


R_C16_crypto_fun2 <- function(x) (x*crypto_phyto_bio1)

R_C16_crypto_bioVol_biweekly <- as.data.frame(apply((R_C16_crypto_biweekly), MARGIN = 1, FUN = R_C16_crypto_fun2))


## sum of biovolume-weighted 2H/1H (R) C16:0 values for each sampling date


R_C16_phyto_all_biweekly.df <- (R_C16_crypto_bioVol_biweekly+ 
                               R_C16_cyano_bioVol_biweekly+ 
                               R_C16_dia_bioVol_biweekly+ 
                               R_C16_dino_bioVol_biweekly+
                               R_C16_GA_bioVol_biweekly+ 
                               R_C16_chryso_bioVol_biweekly)




# modeling R phytol values 

## defining relative biovolume of single algal groups 

cyano_phyto_bio2 <- as.data.frame(phyto_rel.bioVol.dec$cyanobacteria_relBio)

GA_phyto_bio2 <- as.data.frame(phyto_rel.bioVol.dec$green.algae_relBio)

chryso_phyto_bio2 <- as.data.frame(phyto_rel.bioVol.dec$Chrysophyta_relBio)

dia_phyto_bio2 <- as.data.frame(phyto_rel.bioVol.dec$Diatoms_relBio)

dino_phyto_bio2 <- as.data.frame(phyto_rel.bioVol.dec$Dinoflagellates_relBio)

crypto_phyto_bio2 <- as.data.frame(phyto_rel.bioVol.dec$Cryptophyceae_relBio)


#cyanobacteria

R_phytol_cyano_fun1 <- function(x) (x*norm_cyano_alpha_phytol_water.df)

R_phytol_cyano_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_phytol_cyano_fun1)) 


R_phytol_cyano_fun2 <- function(x) (x*cyano_phyto_bio2)

R_phytol_cyano_bioVol_biweekly <- as.data.frame(apply((R_phytol_cyano_biweekly), MARGIN = 1, FUN = R_phytol_cyano_fun2))



## green algae (GA)

R_phytol_GA_fun1 <- function(x) (x*norm_GA_alpha_phytol_water.df)

R_phytol_GA_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_phytol_GA_fun1)) 


R_phytol_GA_fun2 <- function(x) (x*GA_phyto_bio2)

R_phytol_GA_bioVol_biweekly <- as.data.frame(apply((R_phytol_GA_biweekly), MARGIN = 1, FUN = R_phytol_GA_fun2))



## Chrysophyta

R_phytol_chryso_fun1 <- function(x) (x*norm_chryso_alpha_phytol_water.df)

R_phytol_chryso_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_phytol_chryso_fun1)) 


R_phytol_chryso_fun2 <- function(x) (x*chryso_phyto_bio2)

R_phytol_chryso_bioVol_biweekly <- as.data.frame(apply((R_phytol_chryso_biweekly), MARGIN = 1, FUN = R_phytol_chryso_fun2))


## Diatoms

R_phytol_dia_fun1 <- function(x) (x*norm_dia_alpha_phytol_water.df)

R_phytol_dia_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_phytol_dia_fun1)) 


R_phytol_dia_fun2 <- function(x) (x*dia_phyto_bio2)

R_phytol_dia_bioVol_biweekly <- as.data.frame(apply((R_phytol_dia_biweekly), MARGIN = 1, FUN = R_phytol_dia_fun2))



## Dinoflagellates

R_phytol_dino_fun1 <- function(x) (x*norm_dino_alpha_phytol_water.df)

R_phytol_dino_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_phytol_dino_fun1)) 


R_phytol_dino_fun2 <- function(x) (x*dino_phyto_bio2)

R_phytol_dino_bioVol_biweekly <- as.data.frame(apply((R_phytol_dino_biweekly), MARGIN = 1, FUN = R_phytol_dino_fun2))



## Cryptophyceae

R_phytol_crypto_fun1 <- function(x) (x*norm_crypto_alpha_phytol_water.df)

R_phytol_crypto_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_phytol_crypto_fun1)) 


R_phytol_crypto_fun2 <- function(x) (x*crypto_phyto_bio2)

R_phytol_crypto_bioVol_biweekly <- as.data.frame(apply((R_phytol_crypto_biweekly), MARGIN = 1, FUN = R_phytol_crypto_fun2))



#sum of weighted R phytol values for each sampling date

R_phytol_all_biweekly.df <- (R_phytol_crypto_bioVol_biweekly + 
                            R_phytol_cyano_bioVol_biweekly + 
                            R_phytol_dia_bioVol_biweekly + 
                            R_phytol_dino_bioVol_biweekly +
                            R_phytol_GA_bioVol_biweekly + 
                            R_phytol_chryso_bioVol_biweekly)



#modeling R sterol values 

## defining relative biovolume of single eukaryotic algal groups (cyanobacteria do not produce sterols)

GA_eukary_bio <- as.data.frame(eukary.algae_rel.bioVol.dec$green.algae_relBio)

chryso_eukary_bio <- as.data.frame(eukary.algae_rel.bioVol.dec$Chrysophyta_relBio)

dia_eukary_bio <- as.data.frame(eukary.algae_rel.bioVol.dec$Diatoms_relBio)

dino_eukary_bio <- as.data.frame(eukary.algae_rel.bioVol.dec$Dinoflagellates_relBio)

crypto_eukary_bio <- as.data.frame(eukary.algae_rel.bioVol.dec$Cryptophyceae_relBio)


## green algae (GA)

R_sterol_GA_fun1 <- function(x) (x*norm_GA_alpha_sterol_water.df)

R_sterol_GA_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_sterol_GA_fun1)) 


R_sterol_GA_fun2 <- function(x) (x*GA_eukary_bio)

R_sterol_GA_bioVol_biweekly <- as.data.frame(apply((R_sterol_GA_biweekly), MARGIN = 1, FUN = R_sterol_GA_fun2))


## Chrysophyta 

R_sterol_chryso_fun1 <- function(x) (x*norm_chryso_alpha_sterol_water.df)

R_sterol_chryso_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_sterol_chryso_fun1)) 


R_sterol_chryso_fun2 <- function(x) (x*chryso_eukary_bio)

R_sterol_chryso_bioVol_biweekly <- as.data.frame(apply((R_sterol_chryso_biweekly), MARGIN = 1, FUN = R_sterol_chryso_fun2))


## Diatoms

R_sterol_dia_fun1 <- function(x) (x*norm_dia_alpha_sterol_water.df)

R_sterol_dia_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_sterol_dia_fun1)) 


R_sterol_dia_fun2 <- function(x) (x*dia_eukary_bio)

R_sterol_dia_bioVol_biweekly <- as.data.frame(apply((R_sterol_dia_biweekly), MARGIN = 1, FUN = R_sterol_dia_fun2))


## Dinoflagellates

R_sterol_dino_fun1 <- function(x) (x*norm_dino_alpha_sterol_water.df)

R_sterol_dino_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_sterol_dino_fun1)) 


R_sterol_dino_fun2 <- function(x) (x*dino_eukary_bio)

R_sterol_dino_bioVol_biweekly <- as.data.frame(apply((R_sterol_dino_biweekly), MARGIN = 1, FUN = R_sterol_dino_fun2))


## Cryptophyceae

R_sterol_crypto_fun1 <- function(x) (x*norm_crypto_alpha_sterol_water.df)

R_sterol_crypto_biweekly <- as.data.frame(apply((R.water), MARGIN = 1, FUN = R_sterol_crypto_fun1)) 


R_sterol_crypto_fun2 <- function(x) (x*crypto_eukary_bio)

R_sterol_crypto_bioVol_biweekly <- as.data.frame(apply((R_sterol_crypto_biweekly), MARGIN = 1, FUN = R_sterol_crypto_fun2))



#sum of weighted 2H/1H (R) sterol values for each sampling date

R_sterol_eukary_biweekly.df <- (R_sterol_crypto_bioVol_biweekly + 
                               R_sterol_dia_bioVol_biweekly + 
                               R_sterol_dino_bioVol_biweekly +
                               R_sterol_GA_bioVol_biweekly + 
                               R_sterol_chryso_bioVol_biweekly)

```

## calculation of epsilon lipid1/lipid2 values including only algal 2H/1H (R) lipid values (epsilon lipid1/lipid2 phyto)

```{r}
## Epsilon lipid1/lipid2 = ((R lipid1/R lipid2) - 1)*1000

# epsilon C16:0/phytol 

epsilon_C16_phytol_phyto_biweekly <- as.data.frame(((R_C16_phyto_all_biweekly.df/R_phytol_all_biweekly.df)-1)*1000)

mean_eps_C16_phytol_phyto_biweekly <- as.data.frame(rowMeans(epsilon_C16_phytol_phyto_biweekly)) #extract mean
sd_eps_C16_phytol_phyto_biweekly <- as.data.frame(apply(epsilon_C16_phytol_phyto_biweekly, 1, sd)) #extract SD 


# epsilon C16:0/sterol

epsilon_C16_sterol_phyto_biweekly <- as.data.frame(((R_C16_phyto_all_biweekly.df/R_sterol_eukary_biweekly.df)-1)*1000)

mean_eps_C16_sterol_phyto_biweekly <- as.data.frame(rowMeans(epsilon_C16_sterol_phyto_biweekly)) #extract mean 
sd_eps_C16_sterol_phyto_biweekly <- as.data.frame(apply(epsilon_C16_sterol_phyto_biweekly, 1, sd)) #extract SD

# epsilon sterol/phytol

epsilon_sterol_phytol_phyto_biweekly<- as.data.frame(((R_sterol_eukary_biweekly.df/R_phytol_all_biweekly.df)-1)*1000)

mean_eps_sterol_phytol_phyto_biweekly <- as.data.frame(rowMeans(epsilon_sterol_phytol_phyto_biweekly)) #extract mean 
sd_eps_sterol_phytol_phyto_biweekly <- as.data.frame(apply(epsilon_sterol_phytol_phyto_biweekly, 1, sd)) #extract SD


# creating data frame with modeled epsilon lipid1/lipid2 autotroph values (mean and SD)

eps_lipid1.2_modeled_phyto_biweekly <- cbind.data.frame(mean_eps_C16_phytol_phyto_biweekly,
                                                        sd_eps_C16_phytol_phyto_biweekly,
                                                        mean_eps_C16_sterol_phyto_biweekly,
                                                        sd_eps_C16_sterol_phyto_biweekly,
                                                        mean_eps_sterol_phytol_phyto_biweekly,
                                                        sd_eps_sterol_phytol_phyto_biweekly)

colnames(eps_lipid1.2_modeled_phyto_biweekly) <- c("mean_eps_C16_phytol_phyto", "sd_eps_C16_phytol_phyto",
                                                   "mean_eps_C16_sterol_phyto", "sd_eps_C16_sterol_phyto",
                                                   "mean_eps_sterol_phytol_phyto", "sd_eps_sterol_phytol_phyto")

rownames(eps_lipid1.2_modeled_phyto_biweekly) <- rownames(epsilon_lipid1.2)

```

## modeling of theoretical microzooplankton 2H/1H (R) C16:0 and d2H sterol values

```{r}

# estimation of hydrogen isotope fractionation factor alpha between C16:0 of seston and zooplankton 

##  alpha = (d2H lipid zoo+1000)/(d2H lipid seston+1000)

# d2H C16:0 values from seston and zooplankton (Pilecky et al., 2022) [https://doi.org/10.1111/1365-2435.13981]

d2H_C16_seston <- d2H_C16.0_seston_zoo[1:109,]

d2H_C16_zoo <- d2H_C16.0_seston_zoo[110:263,]

## Monte Carlo simulation of d2H C16:0 values for seston and zooplankton 

## N(d2H C16:0) with mean and SD of d2H C16:0 values from Pilecky et al., 2022 (n= 10,000)

## seston

mean_d2H_C16_seston <- mean(d2H_C16_seston$d2H) 
sd_d2H_C16_seston <- sd(d2H_C16_seston$d2H)

norm_d2H_C16_seston <- rnorm(50000, mean= mean_d2H_C16_seston, sd= sd_d2H_C16_seston)

## zooplankton

mean_d2H_C16_zoo <- mean(d2H_C16_zoo$d2H) 
sd_d2H_C16_zoo <- sd(d2H_C16_zoo$d2H) 

norm_d2H_C16_zoo <- rnorm(50000, mean= mean_d2H_C16_zoo, sd= sd_d2H_C16_zoo)


#calculating fractionation factor alpha

fractionation_zoo_seston <- as.data.frame(((norm_d2H_C16_zoo+1000)/(norm_d2H_C16_seston+1000)))


#calculation of theoretical microzooplankton 2H/1H (R) C16:0 and sterol values by multiplying algal R lipid values with alpha 

fractionation_fun <- function(x)(x*t(fractionation_zoo_seston))

## R C16:0 

R_C16_micro_biweekly <- as.data.frame(t(apply(R_C16_phyto_all_biweekly.df, MARGIN= 1, fractionation_fun)))

## R sterol 

R_sterol_micro_biweekly <- as.data.frame(t(apply(R_sterol_eukary_biweekly.df, MARGIN= 1, fractionation_fun)))

```

## modeling of biovolume-weighted 2H/1H (R) lipid values for each sampling date considering algal and microzooplankton biovolume

### calculating 2H/1H (R) lipid values for each group by R lipid = alpha lipid/water * R water, based on R water values in Rotsee, then multiply with relative biovolume

#### first: R lipid group= alpha lipid/water x R water
#### second: R lipid phyto&zoo =  Rlipid group x bioVol 

```{r}

#modeling R C16:0 values

## defining relative biovolume of single algal and microzooplankton groups

cyano_bio_mix <- as.data.frame(phyto.micro_rel.bioVol.dec$cyanobacteria_relBio)

GA_bio_mix <- as.data.frame(phyto.micro_rel.bioVol.dec$green.algae_relBio)

chryso_bio_mix <- as.data.frame(phyto.micro_rel.bioVol.dec$Chrysophyta_relBio)

dia_bio_mix <- as.data.frame(phyto.micro_rel.bioVol.dec$Diatoms_relBio)

dino_bio_mix<- as.data.frame(phyto.micro_rel.bioVol.dec$Dinoflagellates_relBio)

crypto_bio_mix <- as.data.frame(phyto.micro_rel.bioVol.dec$Cryptophyceae_relBio)

roti_bio_mix <- as.data.frame(phyto.micro_rel.bioVol.dec$Rotifera_relBio)

cili_bio_mix <- as.data.frame(phyto.micro_rel.bioVol.dec$Ciliata_relBio)

gym_helv_bio_mix <- as.data.frame(phyto.micro_rel.bioVol.dec$Gymnodinium_helveticum_relBio)


#phytoplankton 

#cyanobacteria

R_C16_cyano_fun3 <- function(x) (x*cyano_bio_mix)

R_C16_cyano_mix_bioVol_biweekly <- as.data.frame(apply((R_C16_cyano_biweekly), MARGIN = 1, FUN = R_C16_cyano_fun3))


## green algae (GA)

R_C16_GA_fun3 <- function(x) (x*GA_bio_mix)

R_C16_GA_mix_bioVol_biweekly <- as.data.frame(apply((R_C16_GA_biweekly), MARGIN = 1, FUN = R_C16_GA_fun3))


## Chrysophyta

R_C16_chryso_fun3 <- function(x) (x*chryso_bio_mix)

R_C16_chryso_mix_bioVol_biweekly <- as.data.frame(apply((R_C16_chryso_biweekly), MARGIN = 1, FUN = R_C16_chryso_fun3))


## Diatoms

R_C16_dia_fun3 <- function(x) (x*dia_bio_mix)

R_C16_dia_mix_bioVol_biweekly <- as.data.frame(apply((R_C16_dia_biweekly), MARGIN = 1, FUN = R_C16_dia_fun3))


## Dinoflagellates

R_C16_dino_fun3 <- function(x) (x*dino_bio_mix)

R_C16_dino_mix_bioVol_biweekly <- as.data.frame(apply((R_C16_dino_biweekly), MARGIN = 1, FUN = R_C16_dino_fun3))


## Cryptophyceae

R_C16_crypto_fun3 <- function(x) (x*crypto_bio_mix)

R_C16_crypto_mix_bioVol_biweekly <- as.data.frame(apply((R_C16_crypto_biweekly), MARGIN = 1, FUN = R_C16_crypto_fun3))


# microzooplankton 

## Rotifera

roti_bio_mix_fun <- function (x) (x*roti_bio_mix)

R_C16_roti_mix_bioVol_biweekly <- as.data.frame(apply(R_C16_micro_biweekly, MARGIN = 2, roti_bio_mix_fun))


## Ciliata

cili_bio_mix_fun <- function(x)(x*cili_bio_mix)

R_C16_cili_mix_bioVol_biweekly <- as.data.frame(apply(R_C16_micro_biweekly, MARGIN = 2, cili_bio_mix_fun))


## Gymnodinium helveticum

gym_helv_bio_mix_fun <- function(x)(x*gym_helv_bio_mix)

R_C16_gym_mix_bioVol_biweekly <- as.data.frame(apply(R_C16_micro_biweekly, MARGIN = 2, gym_helv_bio_mix_fun))


#sum of weighted R C16:0 values for each sampling date (phytoplankton groups + microzooplankton -> 'mix')

R_C16_mix_biweekly.df <- (R_C16_crypto_mix_bioVol_biweekly + 
                         R_C16_cyano_mix_bioVol_biweekly + 
                         R_C16_dia_mix_bioVol_biweekly + 
                         R_C16_dino_mix_bioVol_biweekly +
                         R_C16_GA_mix_bioVol_biweekly + 
                         R_C16_chryso_mix_bioVol_biweekly+
                         R_C16_roti_mix_bioVol_biweekly+
                         R_C16_cili_mix_bioVol_biweekly+
                         R_C16_gym_mix_bioVol_biweekly)


# modeling R sterol values 

## defining relative biovolume of single eukaryotic algal and microzooplankton groups

GA_eukary_mix <- as.data.frame(eukary.algae.micro_rel.bioVol.dec$green.algae_relBio)

chryso_eukary_mix <- as.data.frame(eukary.algae.micro_rel.bioVol.dec$Chrysophyta_relBio)

dia_eukary_mix <- as.data.frame(eukary.algae.micro_rel.bioVol.dec$Diatoms_relBio)

dino_eukary_mix <- as.data.frame(eukary.algae.micro_rel.bioVol.dec$Dinoflagellates_relBio)

crypto_eukary_mix <- as.data.frame(eukary.algae.micro_rel.bioVol.dec$Cryptophyceae_relBio)

roti_eukary_mix <- as.data.frame(eukary.algae.micro_rel.bioVol.dec$Rotifera_relBio)

cili_eukary_mix <- as.data.frame(eukary.algae.micro_rel.bioVol.dec$Ciliata_relBio)

gym_helv_eukary_mix <- as.data.frame(eukary.algae.micro_rel.bioVol.dec$Gymnodinium_helveticum_relBio)


#eukaryotic algae

## green algae (GA)

R_sterol_GA_fun3 <- function(x) (x*GA_eukary_mix)

R_sterol_GA_mix_bioVol_biweekly <- as.data.frame(apply((R_sterol_GA_biweekly), MARGIN = 1, FUN = R_sterol_GA_fun3))


## Chrysophyta

R_sterol_chryso_fun3 <- function(x) (x*chryso_eukary_mix)

R_sterol_chryso_mix_bioVol_biweekly <- as.data.frame(apply((R_sterol_chryso_biweekly), MARGIN = 1, FUN = R_sterol_chryso_fun3))


## Diatoms

R_sterol_dia_fun3 <- function(x) (x*dia_eukary_mix)

R_sterol_dia_mix_bioVol_biweekly <- as.data.frame(apply((R_sterol_dia_biweekly), MARGIN = 1, FUN = R_sterol_dia_fun3))


## Dinoflagellates

R_sterol_dino_fun3 <- function(x) (x*dino_eukary_mix)

R_sterol_dino_mix_bioVol_biweekly <- as.data.frame(apply((R_sterol_dino_biweekly), MARGIN = 1, FUN = R_sterol_dino_fun3))


## Cryptophyceae

R_sterol_crypto_fun3 <- function(x) (x*crypto_eukary_mix)

R_sterol_crypto_mix_bioVol_biweekly <- as.data.frame(apply((R_sterol_crypto_biweekly), MARGIN = 1, FUN = R_sterol_crypto_fun3))


#microzooplankton

## Rotifera

roti_eukary_mix_fun <- function(x)(x*roti_eukary_mix)

R_sterol_roti_mix_bioVol_biweekly <- as.data.frame(apply(R_sterol_micro_biweekly, MARGIN= 2, roti_eukary_mix_fun))


## Ciliata

cili_eukary_mix_fun <- function(x)(x*cili_eukary_mix)

R_sterol_cili_mix_bioVol_biweekly <- as.data.frame(apply(R_sterol_micro_biweekly, MARGIN= 2, cili_eukary_mix_fun))


## Gymnodinium helveticum

gym_helv_eukary_mix_fun <- function(x) (x*gym_helv_eukary_mix)

R_sterol_gym_mix_bioVol_biweekly <- as.data.frame(apply(R_sterol_micro_biweekly, MARGIN= 2, gym_helv_eukary_mix_fun))



#sum of weighted R sterol values for each sampling date (eukaryotic algal groups + microzooplankton -> 'mix')

R_sterol_mix_biweekly.df <- (R_sterol_crypto_mix_bioVol_biweekly +
                            R_sterol_dia_mix_bioVol_biweekly + 
                            R_sterol_dino_mix_bioVol_biweekly +
                            R_sterol_GA_mix_bioVol_biweekly + 
                            R_sterol_chryso_mix_bioVol_biweekly+
                            R_sterol_roti_mix_bioVol_biweekly+
                            R_sterol_cili_mix_bioVol_biweekly+
                            R_sterol_gym_mix_bioVol_biweekly)
```

## calculation of epsilon lipid1/lipid2 values including algal and microzooplankton 2H/1H (R) lipid values (epsilon lipid1/lipid2 phyto&zoo)

```{r}

# epsilon C16:0/phytol 

epsilon_C16_phytol_mix_biweekly <- as.data.frame(((R_C16_mix_biweekly.df/R_phytol_all_biweekly.df)-1)*1000) 

mean_eps_C16_phytol_mix_biweekly <- as.data.frame(rowMeans(epsilon_C16_phytol_mix_biweekly)) #extract mean
sd_eps_C16_phytol_mix_biweekly <- as.data.frame(apply(epsilon_C16_phytol_mix_biweekly, 1, sd)) #extract SD


# epsilon C16:0/sterol

epsilon_C16_sterol_mix_biweekly <- as.data.frame(((R_C16_mix_biweekly.df/R_sterol_mix_biweekly.df)-1)*1000) 

mean_eps_C16_sterol_mix_biweekly <- as.data.frame(rowMeans(epsilon_C16_sterol_mix_biweekly)) #extract mean
sd_eps_C16_sterol_mix_biweekly <- as.data.frame(apply(epsilon_C16_sterol_mix_biweekly, 1, sd)) #extract SD

# epsilon sterol/phytol 

epsilon_sterol_phytol_mix_biweekly <-  as.data.frame(((R_sterol_mix_biweekly.df/R_phytol_all_biweekly.df)-1)*1000) 

mean_eps_sterol_phytol_mix_biweekly <- as.data.frame(rowMeans(epsilon_sterol_phytol_mix_biweekly)) #extract mean
sd_eps_sterol_phytol_mix_biweekly <- as.data.frame(apply(epsilon_sterol_phytol_mix_biweekly, 1, sd)) #extract SD

# creating data frame with modeled epsilon lipid1/lipid2 auto-/heterotroph values (mean and SD)

eps_lipid1.2_modeled_mix_biweekly <- cbind.data.frame(mean_eps_C16_phytol_mix_biweekly,
                                                      sd_eps_C16_phytol_mix_biweekly,
                                                      mean_eps_C16_sterol_mix_biweekly,
                                                      sd_eps_C16_sterol_mix_biweekly,
                                                      mean_eps_sterol_phytol_mix_biweekly,
                                                      sd_eps_sterol_phytol_mix_biweekly)

colnames(eps_lipid1.2_modeled_mix_biweekly) <- c("mean_eps_C16_phytol_mix", "sd_eps_C16_phytol_mix",
                                                 "mean_eps_C16_sterol_mix", "sd_eps_C16_sterol_mix",
                                                 "mean_eps_sterol_phytol_mix", "sd_eps_sterol_phytol_mix")

rownames(eps_lipid1.2_modeled_mix_biweekly) <- rownames(epsilon_lipid1.2)

```

## goodness-of-fit of simulated vs. measured epsilon lipid1/2 values (Root Mean Square Error (RMSE))

```{r}

#merge data frames of measured and modeled epsilon lipid1/lipid2 values

epsilon_measured_modeled <- cbind.data.frame(epsilon_lipid1.2, 
                                             eps_lipid1.2_modeled_phyto_biweekly, 
                                             eps_lipid1.2_modeled_mix_biweekly)

#calculating RMSE: sqrt(mean((data actual - data predicted)^2))

## epsilon C16:0/phytol

epsilon_C16.0_phytol_measured_modeled <- cbind.data.frame(epsilon_measured_modeled$epsilon_C16.0_phytol,
                                                          epsilon_measured_modeled$mean_eps_C16_phytol_phyto,
                                                          epsilon_measured_modeled$mean_eps_C16_phytol_mix)

epsilon_C16.0_phytol_measured_modeled_woNA <- na.omit(epsilon_C16.0_phytol_measured_modeled) #remove NA values

colnames(epsilon_C16.0_phytol_measured_modeled_woNA) <- c("measured", "modeled_phyto", "modeled_mix")


sqrt(mean((epsilon_C16.0_phytol_measured_modeled_woNA$measured - epsilon_C16.0_phytol_measured_modeled_woNA$modeled_phyto)^2))

sqrt(mean((epsilon_C16.0_phytol_measured_modeled_woNA$measured - epsilon_C16.0_phytol_measured_modeled_woNA$modeled_mix)^2))

## epsilon C16:0/sterol

epsilon_C16.0_sterol_measured_modeled <- cbind.data.frame(epsilon_measured_modeled$epsilon_C16.0_sterol,
                                                          epsilon_measured_modeled$mean_eps_C16_sterol_phyto,
                                                          epsilon_measured_modeled$mean_eps_C16_sterol_mix)

epsilon_C16.0_sterol_measured_modeled_woNA <- na.omit(epsilon_C16.0_sterol_measured_modeled)

colnames(epsilon_C16.0_sterol_measured_modeled_woNA) <- c("measured", "modeled_phyto", "modeled_mix")


sqrt(mean((epsilon_C16.0_sterol_measured_modeled_woNA$measured - epsilon_C16.0_sterol_measured_modeled_woNA$modeled_phyto)^2))

sqrt(mean((epsilon_C16.0_sterol_measured_modeled_woNA$measured - epsilon_C16.0_sterol_measured_modeled_woNA$modeled_mix)^2))

## epsilon sterol/phytol

epsilon_sterol_phytol_measured_modeled <- cbind.data.frame(epsilon_measured_modeled$epsilon_sterol_phytol,
                                                           epsilon_measured_modeled$mean_eps_sterol_phytol_phyto,
                                                           epsilon_measured_modeled$mean_eps_sterol_phytol_mix)

epsilon_sterol_phytol_measured_modeled_woNA <- na.omit(epsilon_sterol_phytol_measured_modeled)

colnames(epsilon_sterol_phytol_measured_modeled_woNA) <- c("measured", "modeled_phyto", "modeled_mix")


sqrt(mean((epsilon_sterol_phytol_measured_modeled_woNA$measured-epsilon_sterol_phytol_measured_modeled_woNA$modeled_phyto)^2))

sqrt(mean((epsilon_sterol_phytol_measured_modeled_woNA$measured - epsilon_sterol_phytol_measured_modeled_woNA$modeled_mix)^2))

```

## plotting measured and modeled epsilon lipid1/lipid2 values

```{r}
#separating surface water (surface) and chlorophyll maximum depth (chlorMax)

## surface water 

#measured epsilon lipid1/lipid2 values

epsilon_C16.0_phytol_surface <- as.data.frame(epsilon_lipid1.2[1:25,1:1])
colnames(epsilon_C16.0_phytol_surface) <- c("epsilon_C16.0_phytol")

epsilon_C16.0_sterol_surface <- as.data.frame(epsilon_lipid1.2[1:25,2:2])
colnames(epsilon_C16.0_sterol_surface) <- c("epsilon_C16.0_sterol")

epsilon_sterol_phytol_surface <- as.data.frame(epsilon_lipid1.2[1:25,3:3])
colnames(epsilon_sterol_phytol_surface) <- c("epsilon_sterol_phytol")

#modeled epsilon lipid1/lipid2 phyto values

epsilon_C16.0_phytol_phyto_surface <- eps_lipid1.2_modeled_phyto_biweekly[1:25,1:2]

epsilon_C16.0_sterol_phyto_surface <- eps_lipid1.2_modeled_phyto_biweekly[1:25,3:4]

epsilon_sterol_phytol_phyto_surface <- eps_lipid1.2_modeled_phyto_biweekly[1:25,5:6]

#modeled epsilon lipid1/lipid2 mix values

epsilon_C16.0_phytol_mix_surface <- eps_lipid1.2_modeled_mix_biweekly[1:25,1:2]

epsilon_C16.0_sterol_mix_surface <- eps_lipid1.2_modeled_mix_biweekly[1:25,3:4]

epsilon_sterol_phytol_mix_surface <- eps_lipid1.2_modeled_mix_biweekly[1:25,5:6]


## chlorophyll maximum depth 

#measured epsilon lipid1/lipid2 values

epsilon_C16.0_phytol_chlorMax <- as.data.frame(epsilon_lipid1.2[26:49,1:1])
colnames(epsilon_C16.0_phytol_chlorMax) <- c("epsilon_C16.0_phytol")

epsilon_C16.0_sterol_chlorMax <- as.data.frame(epsilon_lipid1.2[26:49,2:2])
colnames(epsilon_C16.0_sterol_chlorMax) <- c("epsilon_C16.0_sterol")

epsilon_sterol_phytol_chlorMax <- as.data.frame(epsilon_lipid1.2[26:49,3:3])
colnames(epsilon_sterol_phytol_chlorMax) <- c("epsilon_sterol_phytol")

#modeled epsilon lipid1/lipid2 phyto values

epsilon_C16.0_phytol_phyto_chlorMax <- eps_lipid1.2_modeled_phyto_biweekly[26:49,1:2]

epsilon_C16.0_sterol_phyto_chlorMax <- eps_lipid1.2_modeled_phyto_biweekly[26:49,3:4]

epsilon_sterol_phytol_phyto_chlorMax <- eps_lipid1.2_modeled_phyto_biweekly[26:49,5:6]

#modeled epsilon lipid1/lipid2 mix values

epsilon_C16.0_phytol_mix_chlorMax <- eps_lipid1.2_modeled_mix_biweekly[26:49,1:2]

epsilon_C16.0_sterol_mix_chlorMax <- eps_lipid1.2_modeled_mix_biweekly[26:49,3:4]

epsilon_sterol_phytol_mix_chlorMax <- eps_lipid1.2_modeled_mix_biweekly[26:49,5:6]


#setting sampling dates and variables

#surface water

epsilon_datesA <- c("2019-01-30","2019-02-27", "2019-02-13", "2019-03-13", "2019-03-27", "2019-04-10", "2019-04-24",
                    "2019-05-08","2019-05-22", "2019-06-04", "2019-06-19","2019-07-17", "2019-07-30", "2019-08-14",
                    "2019-09-11", "2019-09-25", "2019-10-09","2019-10-23", "2019-11-06","2019-11-20", "2019-12-04",
                    "2019-12-18", "2020-01-07", "2020-01-21", "2020-02-06")

## measured epsilon lipid1/lipid2 values

rownames(epsilon_C16.0_phytol_surface) <- epsilon_datesA
epsilon_C16.0_phytol_surface$date <- as.Date(rownames(epsilon_C16.0_phytol_surface), "%Y-%m-%d")

rownames(epsilon_C16.0_sterol_surface) <- epsilon_datesA
epsilon_C16.0_sterol_surface$date <- as.Date(rownames(epsilon_C16.0_sterol_surface), "%Y-%m-%d")

rownames(epsilon_sterol_phytol_surface) <- epsilon_datesA
epsilon_sterol_phytol_surface$date <- as.Date(rownames(epsilon_sterol_phytol_surface), "%Y-%m-%d")


## modeled epsilon lipid1/lipid2 phyto values

rownames(epsilon_C16.0_phytol_phyto_surface) <- epsilon_datesA
epsilon_C16.0_phytol_phyto_surface$date <- as.Date(rownames(epsilon_C16.0_phytol_phyto_surface), "%Y-%m-%d")

rownames(epsilon_C16.0_sterol_phyto_surface) <- epsilon_datesA
epsilon_C16.0_sterol_phyto_surface$date <- as.Date(rownames(epsilon_C16.0_sterol_phyto_surface), "%Y-%m-%d")

rownames(epsilon_sterol_phytol_phyto_surface) <- epsilon_datesA
epsilon_sterol_phytol_phyto_surface$date <- as.Date(rownames(epsilon_sterol_phytol_phyto_surface), "%Y-%m-%d")

## modeled epsilon lipid1/lipid2 mix values

rownames(epsilon_C16.0_phytol_mix_surface) <- epsilon_datesA
epsilon_C16.0_phytol_mix_surface$date <- as.Date(rownames(epsilon_C16.0_phytol_mix_surface), "%Y-%m-%d")

rownames(epsilon_C16.0_sterol_mix_surface) <- epsilon_datesA
epsilon_C16.0_sterol_mix_surface$date <- as.Date(rownames(epsilon_C16.0_sterol_mix_surface), "%Y-%m-%d")

rownames(epsilon_sterol_phytol_mix_surface) <- epsilon_datesA
epsilon_sterol_phytol_mix_surface$date <- as.Date(rownames(epsilon_sterol_phytol_mix_surface), "%Y-%m-%d")


#chlorophyll maximum depth

epsilon_datesB <- c("2019-01-30", "2019-02-13", "2019-03-13","2019-03-27",  "2019-04-10", "2019-04-24", "2019-05-08",
                    "2019-05-22","2019-06-04", "2019-06-19", "2019-07-17", "2019-07-30", "2019-08-14","2019-09-11",
                    "2019-09-25", "2019-10-09", "2019-10-23", "2019-11-06","2019-11-20", "2019-12-04","2019-12-18",
                    "2020-01-07", "2020-01-21", "2020-02-06")

## measured epsilon lipid1/lipid2 values

rownames(epsilon_C16.0_phytol_chlorMax) <- epsilon_datesB
epsilon_C16.0_phytol_chlorMax$date <- as.Date(rownames(epsilon_C16.0_phytol_chlorMax), "%Y-%m-%d")
epsilon_C16.0_phytol_chlorMax$variable <- c("epsilon_C16.0_phytol")

rownames(epsilon_C16.0_sterol_chlorMax) <- epsilon_datesB
epsilon_C16.0_sterol_chlorMax$date <- as.Date(rownames(epsilon_C16.0_sterol_chlorMax), "%Y-%m-%d")
epsilon_C16.0_sterol_chlorMax$variable <- c("epsilon_C16.0_sterol")

rownames(epsilon_sterol_phytol_chlorMax) <- epsilon_datesB
epsilon_sterol_phytol_chlorMax$date <- as.Date(rownames(epsilon_sterol_phytol_chlorMax), "%Y-%m-%d")
epsilon_sterol_phytol_chlorMax$variable <- c("epsilon_sterol_phytol")


## modeled epsilon lipid1/lipid2 phyto values

rownames(epsilon_C16.0_phytol_phyto_chlorMax) <- epsilon_datesB
epsilon_C16.0_phytol_phyto_chlorMax$date <- as.Date(rownames(epsilon_C16.0_phytol_phyto_chlorMax), "%Y-%m-%d")
epsilon_C16.0_phytol_phyto_chlorMax$variable <- c("mean_eps_C16_phytol_phyto")

rownames(epsilon_C16.0_sterol_phyto_chlorMax) <- epsilon_datesB
epsilon_C16.0_sterol_phyto_chlorMax$date <- as.Date(rownames(epsilon_C16.0_sterol_phyto_chlorMax), "%Y-%m-%d")
epsilon_C16.0_sterol_phyto_chlorMax$variable <- c("mean_eps_C16_sterol_phyto")

rownames(epsilon_sterol_phytol_phyto_chlorMax) <- epsilon_datesB
epsilon_sterol_phytol_phyto_chlorMax$date <- as.Date(rownames(epsilon_sterol_phytol_phyto_chlorMax), "%Y-%m-%d")
epsilon_sterol_phytol_phyto_chlorMax$variable <- c("mean_eps_sterol_phytol_phyto")

## modeled epsilon lipid1/lipid2 mix values

rownames(epsilon_C16.0_phytol_mix_chlorMax) <- epsilon_datesB
epsilon_C16.0_phytol_mix_chlorMax$date <- as.Date(rownames(epsilon_C16.0_phytol_mix_chlorMax), "%Y-%m-%d")
epsilon_C16.0_phytol_mix_chlorMax$variable <- c("mean_eps_C16_phytol_mix")

rownames(epsilon_C16.0_sterol_mix_chlorMax) <- epsilon_datesB
epsilon_C16.0_sterol_mix_chlorMax$date <- as.Date(rownames(epsilon_C16.0_sterol_mix_chlorMax), "%Y-%m-%d")
epsilon_C16.0_sterol_mix_chlorMax$variable <- c("mean_eps_C16_sterol_mix")

rownames(epsilon_sterol_phytol_mix_chlorMax) <- epsilon_datesB
epsilon_sterol_phytol_mix_chlorMax$date <- as.Date(rownames(epsilon_sterol_phytol_mix_chlorMax), "%Y-%m-%d")
epsilon_sterol_phytol_mix_chlorMax$variable <- c("mean_eps_sterol_phytol_mix")


# surface water

pEps_C16.0_phytol_surface <- ggplot()+ ggtitle("1 m depth", subtitle= "1 m depth")+
  coord_cartesian(x=as.Date(c("2019-01-30", "2020-02-06")), ylim=c(85,415), clip="off")+
  scale_y_continuous(breaks = c(100,200,300,400))+
  annotate("rect", xmin = as.Date("2019-04-19") ,xmax = as.Date("2019-04-29"), ymin = -Inf, ymax = 435, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-07-24") ,xmax = as.Date("2019-08-03"), ymin = -Inf, ymax = 435, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-10-18") ,xmax = as.Date("2019-10-28"), ymin = -Inf, ymax = 435, alpha=0.15, fill="seashell3")+
  geom_ribbon(data= epsilon_C16.0_phytol_phyto_surface, 
              aes(x=date, y= mean_eps_C16_phytol_phyto, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_C16_phytol_phyto-sd_eps_C16_phytol_phyto),
                  ymax=(mean_eps_C16_phytol_phyto+sd_eps_C16_phytol_phyto)), fill="dodgerblue1",
              alpha=0.15)+
  geom_ribbon(data= epsilon_C16.0_phytol_mix_surface, 
              aes(x=date, y= mean_eps_C16_phytol_mix, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_C16_phytol_mix-sd_eps_C16_phytol_mix),
                  ymax=(mean_eps_C16_phytol_mix+sd_eps_C16_phytol_mix)), fill="turquoise1",
              alpha=0.15)+
  geom_line(data= epsilon_C16.0_phytol_phyto_surface, 
            aes(x=date, y= mean_eps_C16_phytol_phyto), color= "dodgerblue3", linewidth=1)+
  geom_line(data= epsilon_C16.0_phytol_mix_surface, 
            aes(x=date, y= mean_eps_C16_phytol_mix), color= "turquoise3", linewidth=1)+
  geom_line(data=epsilon_C16.0_phytol_surface[!is.na(epsilon_C16.0_phytol_surface$epsilon_C16.0_phytol),],
            aes(x = date, y = epsilon_C16.0_phytol), color="navy", linewidth=1.25)+
  ylab(expression(epsilon^{2}*""['C16:0/phytol']~("\u2030")))+ 
  annotate("text",y= 486.5, x= as.Date("2018-11-05"),label="A", size=15, fontface=2, color="black")+
  guides(shape = guide_legend(order=1))+
  theme(axis.line.y = element_line(colour = "black"),
        axis.line.x = element_blank(),
        plot.title= element_text(size=35, face= "bold"),
        plot.subtitle= element_text(size=15, color="white"),
        panel.background = element_blank(),
        axis.text.y = element_text(size=30, color="navy", face="bold"),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=37.5, color="navy", margin=margin(r=20)),
        legend.position = "none",
        strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_blank(),
        plot.margin = unit(c(1.5,0,0,0.5), "cm"))


pEps_C16.0_sterol_surface <- ggplot()+
  coord_cartesian(ylim=c(-115,215), clip="off")+
  scale_y_continuous(breaks = c(-100,0,100,200))+
  annotate("rect", xmin = as.Date("2019-04-19") ,xmax = as.Date("2019-04-29"), ymin = -Inf, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-07-24") ,xmax = as.Date("2019-08-03"),  ymin = -Inf, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-10-18") ,xmax = as.Date("2019-10-28"),  ymin = -Inf, ymax = +Inf, alpha=0.15, fill="seashell3")+
  geom_ribbon(data= epsilon_C16.0_sterol_phyto_surface, 
              aes(x=date, y= mean_eps_C16_sterol_phyto, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_C16_sterol_phyto-sd_eps_C16_sterol_phyto),
                  ymax=(mean_eps_C16_sterol_phyto+sd_eps_C16_sterol_phyto)), fill="slateblue1",
              alpha=0.15)+
  geom_ribbon(data= epsilon_C16.0_sterol_mix_surface, 
              aes(x=date, y= mean_eps_C16_sterol_mix, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_C16_sterol_mix-sd_eps_C16_sterol_mix),
                  ymax=(mean_eps_C16_sterol_mix+sd_eps_C16_sterol_mix)), fill="plum1",
              alpha=0.25)+
  geom_line(data= epsilon_C16.0_sterol_phyto_surface, 
            aes(x=date, y= mean_eps_C16_sterol_phyto), color= "slateblue", linewidth=1)+
  geom_line(data= epsilon_C16.0_sterol_mix_surface, 
            aes(x=date, y= mean_eps_C16_sterol_mix), color= "plum3", linewidth=1)+
  geom_line(data=epsilon_C16.0_sterol_surface[!is.na(epsilon_C16.0_sterol_surface$epsilon_C16.0_sterol),],
            aes(x = date, y = epsilon_C16.0_sterol), color="violetred", linewidth=1.25)+
  ylab(expression(epsilon^{2}*""['C16:0/sterol']~("\u2030")))+ 
  guides(shape = guide_legend(order=1))+
  theme(axis.line.y = element_line(colour = "black"),
        axis.line.x = element_blank(),
        panel.background = element_blank(),
        axis.text.y = element_text(size=30, color="violetred", face="bold"),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=37.5, color="violetred"),
        legend.position = "none",
        strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_blank(),
        plot.margin = unit(c(0,0,0,0.5), "cm"))


pEps_sterol_phytol_surface <- ggplot()+
  coord_cartesian(ylim=c(-15,315), clip="off")+
  scale_y_continuous(breaks = c(0,100,200,300))+
  annotate("rect", xmin = as.Date("2019-04-19") ,xmax = as.Date("2019-04-29"), ymin = -30, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-07-24") ,xmax = as.Date("2019-08-03"), ymin = -30, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-10-18") ,xmax = as.Date("2019-10-28"), ymin = -30, ymax = +Inf, alpha=0.15, fill="seashell3")+
  geom_ribbon(data= epsilon_sterol_phytol_phyto_surface, 
              aes(x=date, y= mean_eps_sterol_phytol_phyto, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_sterol_phytol_phyto-sd_eps_sterol_phytol_phyto),
                  ymax=(mean_eps_sterol_phytol_phyto+sd_eps_sterol_phytol_phyto)), fill="chartreuse1",
              alpha=0.2)+
  geom_ribbon(data= epsilon_sterol_phytol_mix_surface, 
              aes(x=date, y= mean_eps_sterol_phytol_mix, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_sterol_phytol_mix-sd_eps_sterol_phytol_mix),
                  ymax=(mean_eps_sterol_phytol_mix+sd_eps_sterol_phytol_mix)), fill="yellow1",
              alpha=0.25)+
  geom_line(data= epsilon_sterol_phytol_phyto_surface, 
            aes(x=date, y= mean_eps_sterol_phytol_phyto), color= "chartreuse2", linewidth=1)+
  geom_line(data= epsilon_sterol_phytol_mix_surface, 
            aes(x=date, y= mean_eps_sterol_phytol_mix), color= "yellow2", linewidth=1)+
  geom_line(data=epsilon_sterol_phytol_surface[!is.na(epsilon_sterol_phytol_surface$epsilon_sterol_phytol),],
            aes(x = date, y = epsilon_sterol_phytol), color="springgreen4", linewidth=1.25)+
  ylab(expression(epsilon^{2}*""['sterol/phytol']~("\u2030")))+
  guides(shape = guide_legend(order=1))+
  theme(axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        axis.text.y = element_text(size=30, color="springgreen4", face="bold"),
        axis.text.x = element_text(size=30, color="black", face="bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size=37.5, color="springgreen4", margin=margin(r=20)),
        legend.position = "none",
        strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_blank(),
        plot.margin = unit(c(0,0,0.5,0.5), "cm"))


pEpsilon_lipid1.2_surface <- plot_grid(pEps_C16.0_phytol_surface, pEps_C16.0_sterol_surface, pEps_sterol_phytol_surface,
                                       ncol=1, rel_heights = c(1.375,1,1.1), align="v", axis='lr')


# chlorophyll maximum depth

pEps_C16.0_phytol_chlorMax <- ggplot()+ ggtitle("chlorophyll maximum depth", subtitle= "chlorophyll maximum depth")+
  coord_cartesian(x=as.Date(c("2019-01-30", "2020-02-06")), ylim=c(85,415), clip="off")+
  scale_y_continuous(breaks = c(100,200,300,400))+
  annotate("rect", xmin = as.Date("2019-04-19") ,xmax = as.Date("2019-04-29"), ymin = -Inf, ymax = 435, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-06-14") ,xmax = as.Date("2019-06-24"), ymin =-Inf, ymax = 435, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-11-01") ,xmax = as.Date("2019-11-11"), ymin =-Inf, ymax = 435, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-11-15") ,xmax = as.Date("2019-11-25"), ymin =-Inf, ymax = 435, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2020-01-16") ,xmax = as.Date("2020-01-26"), ymin =-Inf, ymax = 435, alpha=0.15, fill="seashell3")+
  geom_ribbon(data= epsilon_C16.0_phytol_phyto_chlorMax, 
              aes(x=date, y= mean_eps_C16_phytol_phyto, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_C16_phytol_phyto-sd_eps_C16_phytol_phyto),
                  ymax=(mean_eps_C16_phytol_phyto+sd_eps_C16_phytol_phyto)), fill="dodgerblue1",
              alpha=0.15)+
  geom_ribbon(data= epsilon_C16.0_phytol_mix_chlorMax, 
              aes(x=date, y= mean_eps_C16_phytol_mix, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_C16_phytol_mix-sd_eps_C16_phytol_mix),
                  ymax=(mean_eps_C16_phytol_mix+sd_eps_C16_phytol_mix)), fill="turquoise1",
              alpha=0.15)+
  geom_line(data= epsilon_C16.0_phytol_phyto_chlorMax, 
            aes(x=date, y= mean_eps_C16_phytol_phyto, color= variable), linewidth=1)+
  geom_line(data= epsilon_C16.0_phytol_mix_chlorMax, 
            aes(x=date, y= mean_eps_C16_phytol_mix, color= variable), linewidth=1)+
  geom_line(data=epsilon_C16.0_phytol_chlorMax[!is.na(epsilon_C16.0_phytol_chlorMax$epsilon_C16.0_phytol),],
            aes(x = date, y = epsilon_C16.0_phytol, color=variable), linewidth=1.25)+
  scale_color_manual(labels=c(epsilon_C16.0_phytol= "measured",
                              mean_eps_C16_phytol_phyto = "phyto modeled",
                              mean_eps_C16_phytol_mix= "phyto&zoo modeled"),
                     values=c(epsilon_C16.0_phytol="navy",
                              mean_eps_C16_phytol_phyto = "dodgerblue3" ,
                              mean_eps_C16_phytol_mix= "turquoise3"),
                     breaks=c("epsilon_C16.0_phytol", "mean_eps_C16_phytol_phyto", "mean_eps_C16_phytol_mix"))+
  ylab(expression(epsilon['C16:0-phytol']~("\211")))+ 
  annotate("text",y= 486.5, x= as.Date("2018-11-15"),label="B", size=15, fontface=2, color="black")+
  annotate("text",y= 147.5, x= as.Date("2020-05-25"),label=expression(RMSE~"= 69"~"\u2030"), size=10, color="dodgerblue3")+
  annotate("text",y= 97.5, x= as.Date("2020-05-25"),label=expression(RMSE~"= 67"~"\u2030"), size=10, color="turquoise3")+
  theme(axis.line.y = element_line(colour = "black"),
        axis.line.x = element_blank(),
        plot.title= element_text(size=35, face= "bold"),
        plot.subtitle= element_text(size=15, color="white"),
        panel.background = element_blank(),
        legend.key = element_blank(),
        legend.text = element_text(size=30, color="black"),
        legend.text.align = 0,
        legend.spacing.y = unit(1, "cm"),
        legend.key.width = unit(2,"cm"),
        legend.title = element_blank(),
        axis.text.y = element_text(size=30, color="navy", face="bold"),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = c(1.325,0.65),
        strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_blank(),
        plot.margin = unit(c(1.5,14.5,0,1), "cm"))+
  guides(color = guide_legend(byrow = TRUE, override.aes = list(linewidth=3)))


pEps_C16.0_sterol_chlorMax <- ggplot()+
  coord_cartesian(x=as.Date(c("2019-01-30", "2020-02-06")), ylim=c(-115,215), clip="off")+
  scale_y_continuous(breaks = c(-100,0,100,200))+
  annotate("rect", xmin = as.Date("2019-04-19") ,xmax = as.Date("2019-04-29"), ymin = -Inf, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-06-14") ,xmax = as.Date("2019-06-24"), ymin = -Inf, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-11-01") ,xmax = as.Date("2019-11-11"), ymin = -Inf, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-11-15") ,xmax = as.Date("2019-11-25"),ymin = -Inf, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2020-01-16") ,xmax = as.Date("2020-01-26"), ymin = -Inf, ymax = +Inf, alpha=0.15, fill="seashell3")+
  geom_ribbon(data= epsilon_C16.0_sterol_phyto_chlorMax, 
              aes(x=date, y= mean_eps_C16_sterol_phyto, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_C16_sterol_phyto-sd_eps_C16_sterol_phyto),
                  ymax=(mean_eps_C16_sterol_phyto+sd_eps_C16_sterol_phyto)), fill="slateblue2",
              alpha=0.15)+
  geom_ribbon(data= epsilon_C16.0_sterol_mix_chlorMax, 
              aes(x=date, y= mean_eps_C16_sterol_mix, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_C16_sterol_mix-sd_eps_C16_sterol_mix),
                  ymax=(mean_eps_C16_sterol_mix+sd_eps_C16_sterol_mix)), fill="plum1",
              alpha=0.25)+
  geom_line(data= epsilon_C16.0_sterol_phyto_chlorMax, 
            aes(x=date, y= mean_eps_C16_sterol_phyto, color= variable), linewidth=1)+
  geom_line(data= epsilon_C16.0_sterol_mix_chlorMax, 
            aes(x=date, y= mean_eps_C16_sterol_mix, color= variable), linewidth=1)+
  geom_line(data=epsilon_C16.0_sterol_chlorMax[!is.na(epsilon_C16.0_sterol_chlorMax$epsilon_C16.0_sterol),],
            aes(x = date, y = epsilon_C16.0_sterol, color=variable), linewidth=1.25)+
  scale_color_manual(labels=c(epsilon_C16.0_sterol= "measured",
                              mean_eps_C16_sterol_phyto = "phyto modeled", 
                              mean_eps_C16_sterol_mix= "phyto&zoo modeled"),
                     values=c(epsilon_C16.0_sterol="violetred",
                              mean_eps_C16_sterol_phyto = "slateblue" ,
                              mean_eps_C16_sterol_mix= "plum3"),
                     breaks=c("epsilon_C16.0_sterol", "mean_eps_C16_sterol_phyto", "mean_eps_C16_sterol_mix"))+
  annotate("text",y= -52.5, x= as.Date("2020-05-25"),label=expression(RMSE~"= 78"~"\u2030"), size=10, color="slateblue")+
  annotate("text",y= -102.5, x= as.Date("2020-05-25"),label=expression(RMSE~"= 78"~"\u2030"), size=10, color="plum3")+
  ylab(expression(epsilon['C16:0-sterol']~("\211")))+ 
  theme(axis.line.y = element_line(colour = "black"),
        axis.line.x = element_blank(),
        panel.background = element_blank(),
        legend.key = element_blank(),
        legend.text = element_text(size=30, color="black"),
        legend.text.align = 0,
        legend.spacing.y = unit(1, "cm"),
        legend.title = element_blank(),
        legend.key.width = unit(2,"cm"),
        axis.text.y = element_text(size=30, color="violetred", face="bold"),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = c(1.325,0.65),
        strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_blank(),
        plot.margin = unit(c(0,14.5,0,1), "cm"))+
  guides(color = guide_legend(byrow = TRUE, override.aes = list(linewidth=3)))


pEps_sterol_phytol_chlorMax <- ggplot()+
  coord_cartesian(x=as.Date(c("2019-01-30", "2020-02-06")),ylim=c(-15,315), clip="off")+
  scale_y_continuous(breaks = c(0,100,200,300))+
  annotate("rect", xmin = as.Date("2019-04-19") ,xmax = as.Date("2019-04-29"), ymin = -30, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-06-14") ,xmax = as.Date("2019-06-24"), ymin = -30, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-11-01") ,xmax = as.Date("2019-11-11"), ymin = -30, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2019-11-15") ,xmax = as.Date("2019-11-25"), ymin = -30, ymax = +Inf, alpha=0.15, fill="seashell3")+
  annotate("rect", xmin = as.Date("2020-01-16") ,xmax = as.Date("2020-01-26"), ymin = -30, ymax = +Inf, alpha=0.15, fill="seashell3")+
  geom_ribbon(data= epsilon_sterol_phytol_phyto_chlorMax, 
              aes(x=date, y= mean_eps_sterol_phytol_phyto, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_sterol_phytol_phyto-sd_eps_sterol_phytol_phyto),
                  ymax=(mean_eps_sterol_phytol_phyto+sd_eps_sterol_phytol_phyto)), fill="chartreuse1",
              alpha=0.2)+
  geom_ribbon(data= epsilon_sterol_phytol_mix_chlorMax, 
              aes(x=date, y= mean_eps_sterol_phytol_mix, xmin=min(date), xmax=max(date),
                  ymin=(mean_eps_sterol_phytol_mix-sd_eps_sterol_phytol_mix),
                  ymax=(mean_eps_sterol_phytol_mix+sd_eps_sterol_phytol_mix)), fill="yellow1",
              alpha=0.25)+
  geom_line(data= epsilon_sterol_phytol_phyto_chlorMax, 
            aes(x=date, y= mean_eps_sterol_phytol_phyto, color= variable), linewidth=1)+
  geom_line(data= epsilon_sterol_phytol_mix_chlorMax, 
            aes(x=date, y= mean_eps_sterol_phytol_mix, color= variable), linewidth=1)+
  geom_line(data=epsilon_sterol_phytol_chlorMax[!is.na(epsilon_sterol_phytol_chlorMax$epsilon_sterol_phytol),],
            aes(x = date, y = epsilon_sterol_phytol, color=variable), linewidth=1.25)+
  scale_color_manual(labels=c(epsilon_sterol_phytol= "measured",
                              mean_eps_sterol_phytol_phyto = "phyto modeled",
                              mean_eps_sterol_phytol_mix= "phyto&zoo modeled"),
                     values=c(epsilon_sterol_phytol="springgreen4",
                              mean_eps_sterol_phytol_phyto = "chartreuse2" ,
                              mean_eps_sterol_phytol_mix= "yellow2"),
                     breaks=c("epsilon_sterol_phytol", "mean_eps_sterol_phytol_phyto", "mean_eps_sterol_phytol_mix"))+
  annotate("text",y= 47.5, x= as.Date("2020-05-25"),label=expression(RMSE~"= 44"~"\u2030"), size=10, color="chartreuse2")+
  annotate("text",y= -2.5, x= as.Date("2020-05-25"),label=expression(RMSE~"= 52"~"\u2030"), size=10, color="yellow3")+
  ylab(expression(epsilon['sterol-phytol']~("\211")))+ 
  theme(axis.line = element_line(colour = "black"),
        panel.background = element_blank(),
        legend.key = element_blank(),
        legend.text = element_text(size=30, color="black"),
        legend.text.align = 0,
        legend.spacing.y = unit(1, "cm"),
        legend.title = element_blank(),
        legend.key.width = unit(2,"cm"),
        axis.text.y = element_text(size=30, color="springgreen4", face="bold"),
        axis.text.x = element_text(size=30, color="black", face="bold"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = c(1.325,0.65),
        strip.background = element_blank(),
        strip.placement = "outside",
        strip.text = element_blank(),
        plot.margin = unit(c(0,14.5,0.5,1), "cm"))+
  guides(color = guide_legend(byrow = TRUE, override.aes = list(linewidth=3)))


pEpsilon_lipid1.2_chlorMax <- plot_grid(pEps_C16.0_phytol_chlorMax, pEps_C16.0_sterol_chlorMax, pEps_sterol_phytol_chlorMax, 
                                        ncol=1, rel_heights = c(1.375,1,1.1),align="v", axis='lr')


Fig6 <- plot_grid(pEpsilon_lipid1.2_surface, pEpsilon_lipid1.2_chlorMax, ncol=2,rel_widths = c(0.7,1), align="h")

```

## Fig.6 

```{r, fig.width = 27.5, fig.height = 15, echo=FALSE}

plot(Fig6)

```

