---
title: "S05_Spearman-correlation_algae_vs_epsilon-Lipid1-Lipid2"
author: "Antonia_Klatt"
date: "2024-08-02"
output: html_document
---

```{r}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(here)
library(ggplot2)
library(reshape2)
library(cowplot)
library(Hmisc)
library(corrplot)
library(ggcorrplot)
library(psych)
library(pBrackets)
library(grid)

#import data 

## epsilon lipid1/lipid2 values

epsilon_lipid1.2 <- read.csv(here("01_Data","epsilon_lipid1_lipid2_ROT19.csv"), header = TRUE , sep = ";" , stringsAsFactors = FALSE, na.strings = "#NV")


## phytoplankton relative biovolume 

phytoplankton_rel.bioVol <- read.csv(here("01_Data","phytoplankton_rel_biovolume_ROT19.csv"), header = TRUE , sep = ";" , stringsAsFactors = FALSE, na.strings = "#NV")

### adding sum of cyanobacterial and green algal biovolume

phytoplankton_rel.bioVol$sum_cyano_green.algae <- rowSums(phytoplankton_rel.bioVol[,2:3]) 


## eukaryotic algae relative biovolume 

eukary.algae_rel.bioVol <- read.csv(here("01_Data","eukaryotic_algae_rel_biovolume_ROT19.csv"), header = TRUE , sep = ";" , stringsAsFactors = FALSE, na.strings = "#NV")


#note: data frames include two different depths: surface water (A) and chlorophyll maximum depth (B)


#merge data frames

## epsilon C16:0/phytol values and phytoplankton biovolume

phytoplankton_eps_C16.0_phytol <- cbind.data.frame(phytoplankton_rel.bioVol[,2:8], epsilon_lipid1.2[,2:2])

colnames(phytoplankton_eps_C16.0_phytol) <- c("cyanobacteria", "green.algae", "Chrysophyta", "Diatoms", "Dinoflagellates",
                                              "Cryptophyceae", "sum_cyano_green.algae", "epsilon_C16.0_phytol")

summary(lm(sum_cyano_green.algae~epsilon_C16.0_phytol, data=phytoplankton_eps_C16.0_phytol))

## epsilon C16:0/sterol,epsilon sterol/phytol values and eukaryotic algal biovolume

eukary.algae_eps_C16.0_sterol_phytol <- cbind.data.frame(eukary.algae_rel.bioVol[,2:6], epsilon_lipid1.2[,3:4])

colnames(eukary.algae_eps_C16.0_sterol_phytol) <- c("green.algae", "Chrysophyta", "Diatoms", "Dinoflagellates",
                                                    "Cryptophyceae", "epsilon_C16.0_sterol", "epsilon_sterol_phytol")


#separating surface water (surface) and chlorophyll maximum depth (chlorMax)

phytoplankton_eps_C16.0_phytolA <- phytoplankton_eps_C16.0_phytol[1:25,]
phytoplankton_eps_C16.0_phytolB <- phytoplankton_eps_C16.0_phytol[26:49,]

eukary.algae_eps_C16.0_sterol_phytolA <- eukary.algae_eps_C16.0_sterol_phytol[1:25,]
eukary.algae_eps_C16.0_sterol_phytolB <- eukary.algae_eps_C16.0_sterol_phytol[26:49,]

```

## checking Spearman's correlation between epsilon C16:0/phytol values and phytoplankton biovolume

```{r}
## both depths

#rcor1 <- rcorr(as.matrix(na.omit(phytoplankton_eps_C16.0_phytol)),  type=c("spearman"), )

rcor1 <- corr.test(as.matrix(na.omit(phytoplankton_eps_C16.0_phytol)), method="spearman", adjust="bonferroni")

###correlation matrix indicating significant correlation at significance level alpha 0.05  

corrplot(rcor1$r,  title= "1 m depth + chlorophyll maximum depth", type="upper", p.mat = rcor1$p, diag= FALSE,
         method="ellipse", sig.level = 0.05, insig= "label_sig", tl.col="black", addCoef.col= "black",number.cex = 1,
         number.font = 0.8, col=colorRampPalette(c("lightcyan4","seashell1","lightgoldenrod"))(100))

## surface water

rcor2 <- corr.test(as.matrix(na.omit(phytoplankton_eps_C16.0_phytolA)), method="spearman", adjust="bonferroni")

###correlation matrix indicating significant correlation at significance level alpha 0.05  

corrplot(rcor2$r,  title= "1 m depth", type="upper", p.mat = rcor2$p, diag= FALSE, method="ellipse",
         sig.level = 0.05, insig= "label_sig", tl.col="black", addCoef.col= "black",number.cex = 1, number.font = 0.8,
          col=colorRampPalette(c("lightcyan4","seashell1","lightgoldenrod"))(100))

## chlorophyll maximum depth

rcor3 <- corr.test(as.matrix(na.omit(phytoplankton_eps_C16.0_phytolB)), method="spearman", adjust="bonferroni")

###correlation matrix indicating significant correlation at significance level alpha 0.05  

corrplot(rcor3$r,  title= "chlorophyll maximum depth", type="upper", p.mat = rcor3$p, diag= FALSE, method="ellipse",
         sig.level = 0.05, insig= "label_sig", tl.col="black", addCoef.col= "black",number.cex = 1, number.font = 0.8,
          col=colorRampPalette(c("lightcyan4","seashell1","lightgoldenrod"))(100))

```

## checking Spearman's correlation between epsilon C16:0/sterol,epsilon sterol/phytol values and eukaryotic algal biovolume

```{r}

## both depths

rcor4 <- corr.test(as.matrix(na.omit(eukary.algae_eps_C16.0_sterol_phytol)), method="spearman", adjust="bonferroni")

###correlation matrix indicating significant correlation at significance level alpha 0.05  

corrplot(rcor4$r,  title= "1 m depth + chlorophyll maximum depth", type="upper", p.mat = rcor4$p, diag= FALSE,
         method="ellipse", sig.level = 0.05, insig= "label_sig", tl.col="black", addCoef.col= "black",number.cex = 1,
         number.font = 0.8, mar=c(0,0,1,0), col=colorRampPalette(c("lightcyan4","seashell1","lightgoldenrod"))(100))

## surface water

rcor5 <- corr.test(as.matrix(na.omit(eukary.algae_eps_C16.0_sterol_phytolA)), method="spearman", adjust="bonferroni")

###correlation matrix indicating significant correlation at significance level alpha 0.05  

corrplot(rcor5$r,  title= "1 m depth", type="upper", p.mat = rcor5$p, diag= FALSE, method="ellipse",
         sig.level = 0.05, insig= "label_sig", tl.col="black", addCoef.col= "black",number.cex = 1, number.font = 0.8,
         mar=c(0,0,1,0), col=colorRampPalette(c("lightcyan4","seashell1","lightgoldenrod"))(100))


## chlorophyll maximum depth

rcor6 <- corr.test(as.matrix(na.omit(eukary.algae_eps_C16.0_sterol_phytolB)), method="spearman", adjust="bonferroni")


###correlation matrix indicating significant correlation at significance level alpha 0.05  

corrplot(rcor6$r,  title= "chlorophyll maximum depth", type="upper", p.mat = rcor6$p, diag= FALSE, method="ellipse",
         sig.level = 0.05, insig= "label_sig", tl.col="black", addCoef.col= "black",number.cex = 1, number.font = 0.8,
         mar=c(0,0,1,0), col=colorRampPalette(c("lightcyan4","seashell1","lightgoldenrod"))(100))

```

## plotting correlation matrix with Spearman's correlation between epsilon C16:0/phytol values and phytoplankton biovolume

```{r}

#Fig. S2

cor1 <- cor(na.omit(phytoplankton_eps_C16.0_phytol), method = "spearman")

#both sampling depths

pcorr1 <- ggcorrplot(cor1, method = "square", type = "lower", hc.order= FALSE, sig.level = 0.05,
                     outline.col = "gray", lab=TRUE, lab_size=6,
                     legend.title= c("Spearman's r"), colors=c("turquoise","seashell1","lightgoldenrod"))+
  scale_y_discrete(position='right', labels=c(cyanobacteria= expression(italic("Cyanophyceae")),
                                              green.algae= expression(italic("Chlorophyceae")),
                                              Chrysophyta= expression(italic("Chrysophyceae")), 
                                              Diatoms= expression(italic("Bacillariophyceae")),
                                              Dinoflagellates= expression(italic("Dinophyceae")),
                                              Cryptophyceae= expression(italic("Cryptophyceae")),
                                              sum_cyano_green.algae= expression(sum(italic("Chloro-, Cyanophyceae")))))+
  scale_x_discrete(labels=c(green.algae= expression(italic("Chlorophyceae")),
                            Chrysophyta= expression(italic("Chrysophyceae")), 
                            Diatoms= expression(italic("Bacillariophyceae")),
                            Dinoflagellates= expression(italic("Dinophyceae")),
                            Cryptophyceae= expression(italic("Cryptophyceae")),
                            sum_cyano_green.algae= expression(sum(italic("Chloro-, Cyanophyceae"))),
                            epsilon_C16.0_phytol= expression(delta^2*H['C16:0 Acid'/'Phytol']~("\u2030"))))+
  labs(title= "1 m depth + chlorophyll maximum depth", subtitle= "spacer")+
  annotate("text",x=-0.35,y=8.425,label="A", size=15,color="black", fontface=2)+
  annotate("text",x=3.375,y=1.08,label="*", size=10,color="black")+
  annotate("text",x=6.375,y=1.08,label="*", size=10,color="black")+
  annotate("text",x=6.375,y=4.08,label="*", size=10,color="black")+
  annotate("text",x=12.45,y=4.15,label="% algal biovolume", size=7.75,color="black", angle=90)+
  guides(fill = guide_colorbar(title.position="top", title.hjust = 0.5))+
  coord_cartesian(xlim=c(1,7),ylim=c(1,7),clip="off")+
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        plot.title=element_text(size=30, color="black", face= "bold"),
        plot.subtitle= element_text(size=15, color="white", face= "bold"),
        axis.text.x = element_text(size=22.5, color="black"),
        axis.text.y = element_text(size=22.5, color="black"),
        legend.text = element_text(size=17.5, color="black"),
        legend.title = element_text(size=22.5, color="black"),
        legend.key.width = unit(1.25, "cm"),
        legend.key.height = unit(1, "cm"),
        legend.direction = "horizontal",
        legend.position= c(0.25,0.75),
        plot.margin = unit(c(0.75,2.5,0.25,3), "cm"))

#surface water

cor2 <- cor(na.omit(phytoplankton_eps_C16.0_phytolA), method = "spearman")

pcorr2 <- ggcorrplot(cor2, method = "square", type = "lower", hc.order= FALSE, sig.level = 0.05,
                     outline.col = "gray", lab=TRUE, lab_size=6,
                     legend.title= c("Spearman's r"), colors=c("turquoise","seashell1","lightgoldenrod"))+
  scale_y_discrete(position='right', labels=c(cyanobacteria= expression(italic("Cyanophyceae")),
                                              green.algae= expression(italic("Chlorophyceae")),
                                              Chrysophyta= expression(italic("Chrysophyceae")), 
                                              Diatoms= expression(italic("Bacillariophyceae")),
                                              Dinoflagellates= expression(italic("Dinophyceae")),
                                              Cryptophyceae= expression(italic("Cryptophyceae")),
                                              sum_cyano_green.algae= expression(sum(italic("Chloro-, Cyanophyceae")))))+
  scale_x_discrete(labels=c(green.algae= expression(italic("Chlorophyceae")),
                            Chrysophyta= expression(italic("Chrysophyceae")), 
                            Diatoms= expression(italic("Bacillariophyceae")),
                            Dinoflagellates= expression(italic("Dinophyceae")),
                            Cryptophyceae= expression(italic("Cryptophyceae")),
                            sum_cyano_green.algae= expression(sum(italic("Chloro-, Cyanophyceae"))),
                            epsilon_C16.0_phytol= expression(delta^2*H['C16:0 Acid'/'Phytol']~("\u2030"))))+
  labs(title= "1 m depth", subtitle= "spacer")+
  annotate("text",x=-0.35,y=8.425,label="B", size=15,color="black", fontface=2)+
  annotate("text",x=6.375,y=2.08,label="*", size=10,color="black")+
  annotate("text",x=12.45,y=4.15,label="% algal biovolume", size=7.75,color="black", angle=90)+
  guides(fill = guide_colorbar(title.position="top", title.hjust = 0.5))+
  coord_cartesian(xlim=c(1,7),ylim=c(1,7),clip="off")+
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        plot.title=element_text(size=30, color="black", face= "bold"),
        plot.subtitle= element_text(size=15, color="white", face= "bold"),
        axis.text.x = element_text(size=22.5, color="black"),
        axis.text.y = element_text(size=22.5, color="black"),
        legend.text = element_text(size=17.5, color="black"),
        legend.title = element_text(size=22.5, color="black"),
        legend.key.width = unit(1.25, "cm"),
        legend.key.height = unit(1, "cm"),
        legend.direction = "horizontal",
        legend.position= c(0.25,0.75),
        plot.margin = unit(c(0.75,2.5,0.25,3), "cm"))

#chlorophyll maximum depth 

cor3 <- cor(na.omit(phytoplankton_eps_C16.0_phytolB), method = "spearman")

pcorr3 <- ggcorrplot(cor3, method = "square", type = "lower", hc.order= FALSE, sig.level = 0.05,
                     outline.col = "gray", lab=TRUE, lab_size=6,
                     legend.title= c("Spearman's r"), colors=c("turquoise","seashell1","lightgoldenrod"))+
  scale_y_discrete(position='right', labels=c(cyanobacteria= expression(italic("Cyanophyceae")),
                                              green.algae= expression(italic("Chlorophyceae")),
                                              Chrysophyta= expression(italic("Chrysophyceae")), 
                                              Diatoms= expression(italic("Bacillariophyceae")),
                                              Dinoflagellates= expression(italic("Dinophyceae")),
                                              Cryptophyceae= expression(italic("Cryptophyceae")),
                                              sum_cyano_green.algae= expression(sum(italic("Chloro-, Cyanophyceae")))))+
  scale_x_discrete(labels=c(green.algae= expression(italic("Chlorophyceae")),
                            Chrysophyta= expression(italic("Chrysophyceae")), 
                            Diatoms= expression(italic("Bacillariophyceae")),
                            Dinoflagellates= expression(italic("Dinophyceae")),
                            Cryptophyceae= expression(italic("Cryptophyceae")),
                            sum_cyano_green.algae= expression(sum(italic("Chloro-, Cyanophyceae"))),
                            epsilon_C16.0_phytol= expression(delta^2*H['C16:0 Acid'/'Phytol']~("\u2030"))))+
  labs(title= "chlorophyll maximum depth", subtitle= "spacer")+
  annotate("text",x=-0.35,y=8.425,label="C", size=15,color="black", fontface=2)+
  annotate("text",x=3.375,y=1.08,label="*", size=10,color="black")+
  annotate("text",x=6.375,y=1.08,label="*", size=10,color="black")+
  annotate("text",x=6.375,y=4.08,label="*", size=10,color="black")+
  annotate("text",x=12.45,y=4.15,label="% algal biovolume", size=7.75,color="black", angle=90)+
  guides(fill = guide_colorbar(title.position="top", title.hjust = 0.5))+
  coord_cartesian(xlim=c(1,7),ylim=c(1,7),clip="off")+
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        plot.title=element_text(size=30, color="black", face= "bold"),
        plot.subtitle= element_text(size=15, color="white", face= "bold"),
        axis.text.x = element_text(size=22.5, color="black"),
        axis.text.y = element_text(size=22.5, color="black"),
        legend.text = element_text(size=17.5, color="black"),
        legend.title = element_text(size=22.5, color="black"),
        legend.key.width = unit(1.25, "cm"),
        legend.key.height = unit(1, "cm"),
        legend.direction = "horizontal",
        legend.position= c(0.25,0.75),
        plot.margin = unit(c(0.75,2.5,0.25,3), "cm"))


FigS7 <- plot_grid(pcorr1, pcorr2, pcorr3, ncol=1, align= "v")

```
## Fig. S7

```{r , fig.width = 12.5, fig.height = 30, echo=FALSE}

plot(FigS7)

```

## plotting correlation matrix with Spearman's correlation between epsilon C16:0/sterol, epsilon sterol/phytol values and eukaryotic algal biovolume

```{r}

#both sampling depths

cor4 <- cor(na.omit(eukary.algae_eps_C16.0_sterol_phytol), method = "spearman")

pcorr4 <- ggcorrplot(cor4, method = "square", type = "lower", hc.order= FALSE, sig.level = 0.05,
                     outline.col = "gray", lab=TRUE, lab_size=8, legend.title= c("Spearman's r"),
                     colors=c("turquoise","seashell1","lightgoldenrod"))+
  scale_y_discrete(position='right', labels=c(green.algae= expression(italic("Chlorophyceae")),
                                              Chrysophyta= expression(italic("Chrysophyceae")), 
                                              Diatoms= expression(italic("Bacillariophyceae")),
                                              Dinoflagellates= expression(italic("Dinophyceae")),
                                              Cryptophyceae= expression(italic("Cryptophyceae")),
                                              epsilon_C16.0_sterol=expression(delta^2*H['C16:0 Acid'/'Sterol']~("\u2030"))))+
  scale_x_discrete(labels=c(green.algae= expression(italic("Chlorophyceae")),
                            Chrysophyta= expression(italic("Chrysophyceae")), 
                            Diatoms= expression(italic("Bacillariophyceae")),
                            Dinoflagellates= expression(italic("Dinophyceae")),
                            Cryptophyceae= expression(italic("Cryptophyceae")),
                            epsilon_C16.0_sterol= expression(delta^2*H['C16:0 Acid'/'Sterol']~("\u2030")),
                            epsilon_sterol_phytol= expression(delta^2*H['Sterol'/'Phytol']~("\u2030"))))+
  annotate("text",x=-0.15,y=7.2,label="A", size=15,color="black", fontface=2)+
  labs(title= "1 m depth + chlorophyll maximum depth", subtitle= "spacer")+
  annotate("text",x=6.325,y=6.08,label="*", size=10,color="black")+
  annotate("text",x=9.5,y=3,label="% eukaryotic algal biovolume", size=8.5,color="black", angle=90)+
  guides(fill = guide_colorbar(title.position="top", title.hjust = 0.5))+
  coord_cartesian(xlim=c(1,6),ylim=c(1,6),clip="off")+
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        plot.title=element_text(size=30, color="black", face= "bold"),
        plot.subtitle= element_text(size=15, color="white", face= "bold"),
        axis.text.x = element_text(size=22.5, color="black"),
        axis.text.y = element_text(size=22.5, color="black"),
        legend.text = element_text(size=17.5, color="black"),
        legend.title = element_text(size=22.5, color="black"),
        legend.key.width = unit(1.25, "cm"),
        legend.key.height = unit(1, "cm"),
        legend.direction = "horizontal",
        legend.position= c(0.25,0.75),
        plot.margin = unit(c(0.75,3,0.25,3), "cm"))

#surface water

cor5 <- cor(na.omit(eukary.algae_eps_C16.0_sterol_phytolA), method = "spearman")

pcorr5 <- ggcorrplot(cor5, method = "square", type = "lower", hc.order= FALSE, sig.level = 0.05,
                     outline.col = "gray", lab=TRUE, lab_size=8, legend.title= c("Spearman's r"),
                     colors=c("turquoise","seashell1","lightgoldenrod"))+
  scale_y_discrete(position='right', labels=c(green.algae= expression(italic("Chlorophyceae")),
                                              Chrysophyta= expression(italic("Chrysophyceae")), 
                                              Diatoms= expression(italic("Bacillariophyceae")),
                                              Dinoflagellates= expression(italic("Dinophyceae")),
                                              Cryptophyceae= expression(italic("Cryptophyceae")),
                                              epsilon_C16.0_sterol=
                                                expression(delta^2*H['C16:0 Acid'/'Sterol']~("\u2030"))))+
  scale_x_discrete(labels=c(green.algae= expression(italic("Chlorophyceae")),
                            Chrysophyta= expression(italic("Chrysophyceae")), 
                            Diatoms= expression(italic("Bacillariophyceae")),
                            Dinoflagellates= expression(italic("Dinophyceae")),
                            Cryptophyceae= expression(italic("Cryptophyceae")),
                            epsilon_C16.0_sterol= expression(delta^2*H['C16:0 Acid'/'Sterol']~("\u2030")),
                            epsilon_sterol_phytol= expression(delta^2*H['Sterol'/'Phytol']~("\u2030"))))+
  annotate("text",x=-0.15,y=7.2,label="B", size=15,color="black", fontface=2)+
  labs(title= "1 m depth", subtitle= "spacer")+
  annotate("text",x=-1,y=7.44,label="B", size=15,color="black", fontface=2)+
  annotate("text",x=6.325,y=6.08,label="*", size=10,color="black")+
  annotate("text",x=9.5,y=3,label="% eukaryotic algal biovolume", size=8.5,color="black", angle=90)+
  guides(fill = guide_colorbar(title.position="top", title.hjust = 0.5))+
  coord_cartesian(xlim=c(1,6),ylim=c(1,6),clip="off")+
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        plot.title=element_text(size=30, color="black", face= "bold"),
        plot.subtitle= element_text(size=15, color="white", face= "bold"),
        axis.text.x = element_text(size=22.5, color="black"),
        axis.text.y = element_text(size=22.5, color="black"),
        legend.text = element_text(size=17.5, color="black"),
        legend.title = element_text(size=22.5, color="black"),
        legend.key.width = unit(1.25, "cm"),
        legend.key.height = unit(1, "cm"),
        legend.direction = "horizontal",
        legend.position= c(0.25,0.75),
        plot.margin = unit(c(0.75,3,0.25,3), "cm"))

#chlorophyll maximum depth

cor6 <- cor(na.omit(eukary.algae_eps_C16.0_sterol_phytolB), method = "spearman")

pcorr6 <- ggcorrplot(cor6, method = "square", type = "lower", hc.order= FALSE, sig.level = 0.05,
                     outline.col = "gray", lab=TRUE, lab_size=8, legend.title= c("Spearman's r"),
                     colors=c("turquoise","seashell1","lightgoldenrod"))+
  scale_y_discrete(position='right', labels=c(green.algae= expression(italic("Chlorophyceae")),
                                              Chrysophyta= expression(italic("Chrysophyceae")), 
                                              Diatoms= expression(italic("Bacillariophyceae")),
                                              Dinoflagellates= expression(italic("Dinophyceae")),
                                              Cryptophyceae= expression(italic("Cryptophyceae")),
                                              epsilon_C16.0_sterol=expression(delta^2*H['C16:0 Acid'/'Sterol']~("\u2030"))))+
  scale_x_discrete(labels=c(green.algae= expression(italic("Chlorophyceae")),
                            Chrysophyta= expression(italic("Chrysophyceae")), 
                            Diatoms= expression(italic("Bacillariophyceae")),
                            Dinoflagellates= expression(italic("Dinophyceae")),
                            Cryptophyceae= expression(italic("Cryptophyceae")),
                            epsilon_C16.0_sterol= expression(delta^2*H['C16:0 Acid'/'Sterol']~("\u2030")),
                            epsilon_sterol_phytol= expression(delta^2*H['Sterol'/'Phytol']~("\u2030"))))+
  annotate("text",x=-0.15,y=7.2,label="C", size=15,color="black", fontface=2)+
  labs(title= "chlorophyll maximum depth", subtitle= "spacer")+
  annotate("text",x=-1,y=7.44,label="B", size=15,color="black", fontface=2)+
  annotate("text",x=4.325,y=2.08,label="*", size=10,color="black")+
  annotate("text",x=6.325,y=6.08,label="*", size=10,color="black")+
  annotate("text",x=9.5,y=3, label="% eukaryotic algal biovolume", size=8.5,color="black", angle=90)+
  guides(fill = guide_colorbar(title.position="top", title.hjust = 0.5))+
  coord_cartesian(xlim=c(1,6),ylim=c(1,6),clip="off")+
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        plot.title=element_text(size=30, color="black", face= "bold"),
        plot.subtitle= element_text(size=15, color="white", face= "bold"),
        axis.text.x = element_text(size=22.5, color="black"),
        axis.text.y = element_text(size=22.5, color="black"),
        legend.text = element_text(size=17.5, color="black"),
        legend.title = element_text(size=22.5, color="black"),
        legend.key.width = unit(1.25, "cm"),
        legend.key.height = unit(1, "cm"),
        legend.direction = "horizontal",
        legend.position= c(0.25,0.75),
        plot.margin = unit(c(0.75,3,0.25,3), "cm"))

FigS8 <- plot_grid(pcorr4, pcorr5, pcorr6, ncol=1, align= "v")
 
```

## Fig. S8

```{r , fig.width = 12.5, fig.height = 30, echo=FALSE}

plot(FigS8)

```
